Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-13 analysis/paper/asymsam.Rmd
Agrega cómputo de los índices ENSO precipitación para responder a review

```{r pp-enso-patterns}

pp_patterns <- enso[index == "oni"] %>% 
  .[pp, on = "time"] %>% 
  .[, precip_a := Anomaly(precip, na.rm = TRUE), by = .(lon, lat, month(time))] %>% 
  .[, index := NULL] %>% 
  .[, lapply(.SD, mean, na.rm = TRUE), by = .(lon, lat, time = seasonally(time))] %>% 
  na.omit() %>% 
  .[, FitLm(precip_a, value), by = .(lon, lat, season(time))] %>% 
  rm_intercept() %>% 
  add_continent() %>% 
  .[continent %in% names(continents)[-1]]

@@

pp_enso_index %>% 
  dcast(time ~ continent) %>% 
  ggplot(aes(oceania, america)) +
  geom_point() +
  facet_wrap(~season(time), scales = "free")

# pp_enso_index %>% 
#   dcast(time ~ continent) %>% 
#   .[, cor(oceania, america), by = season(time)]
```

>>>>

```{r pp-enso-patterns}
# This computation is not part of the paper, but was used as an answer to a reviewr. 
pp_patterns <- enso[index == "oni"] %>% 
  .[pp, on = "time"] %>% 
  .[, precip_a := Anomaly(precip, na.rm = TRUE), by = .(lon, lat, month(time))] %>% 
  .[, index := NULL] %>% 
  .[, lapply(.SD, mean, na.rm = TRUE), by = .(lon, lat, time = seasonally(time))] %>% 
  na.omit() %>% 
  .[, FitLm(precip_a, value), by = .(lon, lat, season(time))] %>% 
  rm_intercept() %>% 
  add_continent() %>% 
  .[continent %in% names(continents)[-1]]

@@

cors_enso_pp <- pp_enso_index %>%
  dcast(time ~ continent) %>%
  .[, cor(oceania, america), by = season(time)] %>% 
  .[, label := paste0(season, " (cor=", signif(V1, 2), ")")]

# pp_enso_index %>% 
#   dcast(time ~ continent) %>% 
#   .[, season := season(time)] %>% 
#   ggplot(aes(oceania, america)) +
#   geom_point() +
#   geom_smooth(method = "lm") +
#   scale_x_continuous("Oceania index") +
#   scale_y_continuous("America Index") +
#   facet_wrap(~season, scales = "free", labeller = labeller(season= setNames(cors_enso_pp$label,
#                                                                             cors_enso_pp$season)))
